

\textbf{The following concerns Group B's getAuthorizationRestrictions use case:}\newline


\textbf{Violations:}
\begin{enumerate}
	\item Pre-conditions:	
	\begin{itemize}
		\item User is Administrator of space for which authorization restrictions are queried
		\begin{itemize}
				\item No validation is done to ensure the user querying the restrictions is an administrator
		\end{itemize}
	\end{itemize}
	
	\item Post-conditions:
	\begin{itemize}
		\item  A GetAuthorizationRestrictionResult object should be returned by the function. 
		\begin{itemize}
				\item Due to the asynchronous nature of Nodejs, the result of the function is undefined when called although the result is later available. The function returns before it has computed a result and no means to return the result synchronously is provided. Therefore this post-condition is violated.
		\end{itemize}
	\end{itemize}
	
	\item Data structure requirement:
	\begin{itemize}
		\item  A GetAuthorizationRestrictionResult object should be returned by the function. 
		\begin{itemize}
				\item The argument passed to GetAuthorizationRestriction in the implementation of Authorization B is a string containing a Buzzspace ID instead of a GetAuthorizationRestrictionRequest object. Therefore this is a datastructure requirement violation.
		\end{itemize}
	\end{itemize}
		
\end{enumerate}

\textbf{Successes:}
\begin{enumerate}
	\item Pre-conditions:	
	\begin{itemize}
		\item Space is active
		\begin{itemize}
				\item The function only selects documents from the database where the delete parameter is false to indicate the space is active.
		\end{itemize}
	\end{itemize}	
\end{enumerate}


\noindent
\medskip

\textbf{Further information on the use case:}
\noindent

The following test cases were tested on the getAuthorizationRestrictions use case:
\begin{enumerate}
	\item User's status points are greater than the service's minimum status points.
	\item User's status points are less than the service's minimum status points.
	\item User does not exist.
  	\item Service does not exist.
  	\item Buzz Space is not active.
  	\item Buzz Space does not exist.
  	\item User is Administrator for Buzz Space.
\end{enumerate}
\medskip
\begin{itemize}
\item The following test cases passed:  5 and 6.
	
\item The following test cases failed: 1, 2, 3, 4 and 7.
	\begin{itemize}
		\item No means is provided to even identify the user of this use-case. Status points of the user can therefore not be compared to the service's minimum status points.
		\item No validation is made to check that the current user actually exists
		\item No validation is made to ensure that the user is an administrator, since no means of even identifying the use-case user is provided.
	\end{itemize}

	\item An implementation summary of the use case is as follows: A restriction is found according to a Buzzspace id provided as an argument to the function. If the space does not exist or is not active a Buzzspace Error exception is thrown. If the space does exist and is active, the restriction objects is returned in the format of its database entry as a JSON. This is however only visible when printed to the console from within the implementation, due to the asynchronous nature of NodeJS.

\item If connection with the database cannot be established a Connection Error exception is thrown.

\end{itemize}